biomass mash

### 2020-12-03 R/Pre_manuscript/Overlap_with_4way_QTL.Rmd
Move R scripts not used in current manuscript and rename those that are

---
title: "D2F_4way_overlap"
author: "Alice MacQueen"
date: 2020-04-22
output: html_document
---

@@

```{r}
mash <- readRDS("~/Github/pvdiv-phenology-gxe/analysis/mash/Gulf_Midwest/Strong_Effects49260SNPs.rds")
qtl <- read_csv(file = "~/Github/pvdiv-phenology-gxe/data/QTLs_with_flank_markers_FL50_7_sites_full_model.csv")
sites <- readRDS("~/Github/pvdiv-phenotypes/data/sites.rds")
```

```{r}
df <- get_significant_results(m=mash) %>%
  enframe(name = "SNP")
df1 <- switchgrassGWAS:::get_marker_df(mash)
df1 <- df1 %>%
  mutate(log10bf = switchgrassGWAS:::get_log10bf(m=mash),
         sigcond = switchgrassGWAS:::get_n_significant_conditions(mash)
         )
effects <- ashr::get_pm(mash)
sd <- ashr::get_psd(mash)
colnames(sd) <- str_replace(colnames(sd), "Bhat", "Shat")

df1 <- cbind(df1, effects, sd)
```

```{r}
qtl %>%
  arrange(desc(lod)) %>%
  dplyr::select(lodcolumn, lod, chr, flank_lo, flank_hi)
```
From most to least significant, for QTL:
	Chr02N_58.039498 61.274395
	Chr05N_1.502713 4.328965
	Chr05N_58.916323 65.990782
	Chr04K_1.959391 5.499253
	Chr02K_63.687871 65.484856
	  Chr09K_13.655791 18.177373
		Chr03K_17.368264	Chr03K_26.170048
		Chr08N_5.54356	Chr08N_34.415808

# Chr02N  58.039498 61.274395
```{r}
switchgrassGWAS::mash_plot_effects(m=mash, i = 11087)
switchgrassGWAS::mash_plot_effects(m=mash, i = 11468)

df1 %>%
  filter(log10bf > 5) # 25 values
df1 %>%
  filter(log10bf > 4) # 93 values (1800 above 2)
```
Close
	Chr02N_58.039498 61.274395
Chr02N_15281005	9405	4.057999	1	
Chr02N_50051440	10742	4.288475	5	5.8214656195	
Chr02N_56422155	11087	5.158628	6	5.9439138054	
Chr02N_57947932	11178	4.390894	6	4.7648643926	
Chr02N_63420472	11467	4.374355	5	5.5078867975	
Chr02N_63420484	11468	5.022484	6	-5.0720890743

Close, first is better
	Chr05N_1.502713 4.328965
	Chr05N_58.916323 65.990782
Chr05N_4512043	25413	5.929161	6	8.5445301065	
Chr05N_20476771	26421	4.303708	5	6.4982493387	
Chr05N_24505333	26560	4.225575	5	7.4869178552	
Chr05N_25731508	26609	4.081614	1	-0.0036192576	
Chr05N_28066146	26673	4.727816	6	8.9999136556	
Chr05N_36999363	26879	5.038580	5	-5.0653499084	
Chr05N_37110671	26885	4.151390	5	6.1070001182	
Chr05N_38945328	26961	4.980246	6
Chr05N_46107016	27330	4.099486	6	3.6428083879	
Chr05N_65588952	28354	4.003577	6

Close
	Chr04K_1.959391 5.499253
Chr04K_1935684	17557	4.235319	5	6.1526138902	
Chr04K_6537440	17814	4.403893	5	4.7144521481	
Chr04K_6567024	17818	4.962056	6	5.1767913940	
Chr04K_8657535	17940	5.205059  6
Chr04K_12651532	18152	6.096971  6

Not close
	Chr02K_63.687871 65.484856
Chr02K_23509869	6711	5.595545	6	-6.7548782752	
Chr02K_23682427	6713	5.430460	5	6.9669557271	
Chr02K_35881338	6882	4.095730	6

```{r}
panela <- df1 %>%
  filter(grepl("Chr02N_(5|6)", Marker) & between(value, 11000, 11500)) %>%
  separate(Marker, into = c("Chr", "_", "Position"), sep = c(6,7), remove = FALSE) %>%
  mutate(Position = as.numeric(Position)) %>%
  ggplot(aes(x=Position, y = log10bf)) +
  geom_point(aes(color = sigcond)) +
  scale_color_viridis(option = "B", end = 0.8) # 26711
save_plot(filename = "Chr02N_58_to_61Mb_D2F_mash_result_zoom.png", plot = panela, base_asp = 1.2)

panelb <- switchgrassGWAS::mash_plot_effects(m=mash, i = 11087)
#panelb <- switchgrassGWAS::mash_plot_effects(m=mash, i = 11467)
##panelb <- switchgrassGWAS::mash_plot_effects(m=mash, i = 11468)
#panelb <- switchgrassGWAS::mash_plot_effects(m=mash, i = 11178)

p3 <- plot_grid(panela, panelb$ggobject, rel_widths = c(2,1))
save_plot(filename = "Chr02N_58_to_61Mb_mash_result_zoom_2panel.png", plot = p3, base_asp = 1.5)
```
# Chr05N 
```{r}

panela <- df1 %>%
  filter(grepl("Chr05N_", Marker) & between(value, 24000, 25600)) %>%
  separate(Marker, into = c("Chr", "_", "Position"), sep = c(6,7), remove = FALSE) %>%
  mutate(Position = as.numeric(Position)) %>%
  ggplot(aes(x=Position, y = log10bf)) +
  geom_point(aes(color = sigcond)) +
  scale_color_viridis(option = "B", end = 0.8) # 26711

panelb <- switchgrassGWAS::mash_plot_effects(m=mash, i = 25413)
#panelb <- switchgrassGWAS::mash_plot_effects(m=mash, i = 11467)
##panelb <- switchgrassGWAS::mash_plot_effects(m=mash, i = 11468)
#panelb <- switchgrassGWAS::mash_plot_effects(m=mash, i = 11178)

(p3 <- plot_grid(panela, panelb$ggobject, rel_widths = c(2,1)))
save_plot(filename = "Chr05N_0_to_8Mb_D2F_mash_result_zoom.png", plot = panela, base_asp = 1.2)
save_plot(filename = "Chr05N_0_to_8Mb_mash_result_zoom_2panel.png", plot = p3, base_asp = 1.5)
```

# Chr05N 60Mb
```{r}

panela <- df1 %>%
  filter(grepl("Chr05N_(5|6)", Marker) & between(value, 28000, 28500)) %>%
  separate(Marker, into = c("Chr", "_", "Position"), sep = c(6,7), remove = FALSE) %>%
  mutate(Position = as.numeric(Position)) %>%
  ggplot(aes(x=Position, y = log10bf)) +
  geom_point(aes(color = sigcond)) +
  scale_color_viridis(option = "B", end = 0.8) # 26711

panelb <- switchgrassGWAS::mash_plot_effects(m=mash, i = 28354)
#panelb <- switchgrassGWAS::mash_plot_effects(m=mash, i = 11467)
##panelb <- switchgrassGWAS::mash_plot_effects(m=mash, i = 11468)
#panelb <- switchgrassGWAS::mash_plot_effects(m=mash, i = 11178)

(p3 <- plot_grid(panela, panelb$ggobject, rel_widths = c(2,1)))
save_plot(filename = "Chr05N_58_to_68Mb_D2F_mash_result_zoom.png", plot = panela, base_asp = 1.2)
save_plot(filename = "Chr05N_58_to_68Mb_mash_result_zoom_2panel.png", plot = p3, base_asp = 1.5)
```

# Chr04K

Close
	Chr04K_1.959391 5.499253
Chr04K_1935684	17557	4.235319	5	6.1526138902	
Chr04K_6537440	17814	4.403893	5	4.7144521481	
Chr04K_6567024	17818	4.962056	6	5.1767913940	
Chr04K_8657535	17940	5.205059  6
Chr04K_12651532	18152	6.096971  6
```{r}

panela <- df1 %>%
  filter(grepl("Chr04K_", Marker) & between(value, 17500, 18200)) %>%
  separate(Marker, into = c("Chr", "_", "Position"), sep = c(6,7), remove = FALSE) %>%
  mutate(Position = as.numeric(Position)) %>%
  ggplot(aes(x=Position, y = log10bf)) +
  geom_point(aes(color = sigcond)) +
  scale_color_viridis(option = "B", end = 0.8) # 26711

panelb <- switchgrassGWAS::mash_plot_effects(m=mash, i = 18152)
#panelb <- switchgrassGWAS::mash_plot_effects(m=mash, i = 17557)
##panelb <- switchgrassGWAS::mash_plot_effects(m=mash, i = 17814)
#panelb <- switchgrassGWAS::mash_plot_effects(m=mash, i = 17818)
 switchgrassGWAS::mash_plot_effects(m=mash, i = 17940)

(p3 <- plot_grid(panela, panelb$ggobject, rel_widths = c(2,1)))
save_plot(filename = "Chr04K_1_to_12Mb_D2F_mash_result_zoom.png", plot = panela, base_asp = 1.2)
save_plot(filename = "Chr04K_1_to_12Mb_mash_result_zoom_2panel.png", plot = p3, base_asp = 1.5)
```

# Chr08N_5.54356	Chr08N_34.415808
```{r}

panela <- df1 %>%
  filter(grepl("Chr08N_", Marker) & between(value, 40000, 41100)) %>%
  separate(Marker, into = c("Chr", "_", "Position"), sep = c(6,7), remove = FALSE) %>%
  mutate(Position = as.numeric(Position)) %>%
  ggplot(aes(x=Position, y = log10bf)) +
  geom_point(aes(color = sigcond)) +
  scale_color_viridis(option = "B", end = 0.8) # 26711

panelb <- switchgrassGWAS::mash_plot_effects(m=mash, i = 40305)
#panelb <- switchgrassGWAS::mash_plot_effects(m=mash, i = 40514)

(p3 <- plot_grid(panela, panelb$ggobject, rel_widths = c(2,1)))
save_plot(filename = "Chr08N_0_to_1Mb_D2F_mash_result_zoom.png", plot = panela, base_asp = 1.2)
save_plot(filename = "Chr08N_0_to_1Mb_mash_result_zoom_2panel.png", plot = p3, base_asp = 1.5)
```

@@

```{r}
i=1
width = 1000000

>>>>

---
title: "FL50_4way_overlap"
author: "Alice MacQueen"
date: "1/21/2020"
output: html_document
---

@@

```{r}
mash <- readRDS("~/Github/pvdiv-phenology-gxe/analysis/FL50/Strong_Effects29475SNPs.rds")
qtl <- read_csv("QTLsWithFlankMarkers_full_multiple_sites.csv")
load("~/Github/pvdiv-phenology-gxe/data/sites.rda")
```

```{r}
df <- get_significant_results(m=mash) %>%
  enframe(name = "SNP")
df1 <- switchgrassGWAS:::get_marker_df(mash)
df1 <- df1 %>%
  mutate(log10bf = switchgrassGWAS:::get_log10bf(m=mash),
         sigcond = switchgrassGWAS:::get_n_significant_conditions(mash)
         )
```

```{r}
switchgrassGWAS:::get_log10bf(m=mash)
switchgrassGWAS::mash_plot_effects(m=mash, i = 26711)

df1 %>%
  filter(log10bf > 5)

panela <- df1 %>%
  filter(grepl("Chr09K_5", Marker) & value > 26500) %>%
  separate(Marker, into = c("Chr", "_", "Position"), sep = c(6,7), remove = FALSE) %>%
  mutate(Position = as.numeric(Position)) %>%
  ggplot(aes(x=Position, y = log10bf)) +
  geom_point(aes(color = sigcond)) +
  scale_color_viridis(option = "B") # 26711
save_plot(filename = "Chr09K_FL50_mash_result_zoom.png", plot = last_plot(), base_asp = 1.5)

p3 <- plot_grid(panela, panelb$ggobject, rel_widths = c(2,1))
save_plot(filename = "Chr09K_FL50_mash_result_zoom_2panel.png", plot = p3, base_asp = 3)
```
#Chr05N
```{r}
panela <- df1 %>%
  filter(grepl("Chr05N_1", Marker) & value > 15717) %>%
  separate(Marker, into = c("Chr", "_", "Position"), sep = c(6,7), remove = FALSE) %>%
  mutate(Position = as.numeric(Position)) %>%
  ggplot(aes(x=Position, y = log10bf)) +
  geom_point(aes(color = sigcond)) +
  scale_color_viridis(option = "B", end = 0.9) 
panelb <- switchgrassGWAS::mash_plot_effects(m=mash, i = 15864)
panelb$ggobject 
p3 <- plot_grid(panela, panelb$ggobject, rel_widths = c(2,1))
save_plot(filename = "Chr05N_FL50_mash_result_zoom.png", plot = p3, base_asp = 3)

```
Chr05N_15045423	15847	4.688166	8	  affects flowering at the 3 major sites
Chr05N_15048576	15849	4.101891	8	
Chr05N_15951722	15863	4.048425	7	  affects flowering at KBSM & CLMB
Chr05N_16084715	15864	4.226715	8	  affects flowering at the 3 major sites

```{r}
panela <- df1 %>%
  filter(grepl("Chr04K_1", Marker) & value > 11158) %>%
  separate(Marker, into = c("Chr", "_", "Position"), sep = c(6,7), remove = FALSE) %>%
  mutate(Position = as.numeric(Position)) %>%
  ggplot(aes(x=Position, y = log10bf)) +
  geom_point(aes(color = sigcond)) +
  scale_color_viridis(option = "B", end = 0.9) 
panelb <- switchgrassGWAS::mash_plot_effects(m=mash, i = 11493)
panelb$ggobject 
p3 <- plot_grid(panela, panelb$ggobject, rel_widths = c(2,1))
save_plot(filename = "Chr04K_FL50_mash_result_zoom.png", plot = p3, base_asp = 3)
df1 %>%
  filter(grepl("Chr04K_1", Marker) & value > 11158 & log10bf > 4)
```
Chr04K_14442056	11332	4.954623	7	
Chr04K_14919129	11382	4.263826	8	qtl
Chr04K_14920267	11384	4.655388	8	
Chr04K_14955235	11388	4.693233	7	
Chr04K_16627327	11460	4.240948	7	
Chr04K_16687695	11493	4.405048	7	
Chr04K_18870690	11610	5.308748	6

@@

```{r}
i=1
width = 200000

### 2020-12-03 R/Pre_manuscript/Visualize_BIOMASS_mash_GxE.Rmd
Move R scripts not used in current manuscript and rename those that are

# Differential Sensitivity
```{r, cache = TRUE}
length(get_significant_results(m))
mash_plot_pairwise_sharing(corrmatrix = gxe$S_DS)
max(gxe$S_DS)
min(gxe$S_DS)
```
`r length(get_significant_results(m))` SNPs have significant effects in the mash analysis. Of those, between `r min(gxe$S_DS)` and `r max(gxe$S_DS)` have differentially significant effects between pairs of conditions.

# Antagonistic Pleiotropy
```{r, cache = TRUE}
mash_plot_pairwise_sharing(corrmatrix = gxe$S_AP)
```
`r length(get_significant_results(m))` SNPs have significant effects in the mash analysis. Of those, between `r min(gxe$S_AP)` and `r max(gxe$S_AP)` have antagonistically pleiotropic effects between pairs of conditions.

@@

>>>>

# Differential Sensitivity
```{r, cache = TRUE}
length(get_significant_results(m))
mash_plot_pairwise_sharing(corrmatrix = gxe$S_all)
max(gxe$S_DS)
min(gxe$S_DS)
```
`r length(get_significant_results(m))` SNPs have significant effects in the mash analysis. Of those, between `r min(gxe$S_DS)` and `r max(gxe$S_DS)` have differentially significant effects between pairs of conditions.

# Antagonistic Pleiotropy
```{r, cache = TRUE}
mash_plot_pairwise_sharing(corrmatrix = gxe$S_AP)
sum(gxe$S_AP)/78411 # 510
sum(gxe$S_DS) # 3188
sum(gxe$S_2_no) # 118913
sum(gxe$S_all) # 130939
sum(gxe$S_CN) # 11516

(sum(gxe$S_AP)/sum(gxe$S_all))*length(get_significant_results(m))
(sum(gxe$S_CN)/sum(gxe$S_all))*length(get_significant_results(m))
(sum(gxe$S_2_no)/sum(gxe$S_all))*length(get_significant_results(m))
(sum(gxe$S_DS)/sum(gxe$S_all))*length(get_significant_results(m))
19780+85+1915+530
length(gxe$S_all)
130939/81
# 21781
# 
mash_plot_pairwise_sharing(corrmatrix = (gxe$S_AP/gxe$S_all))
max((gxe$S_AP/gxe$S_all))
max((gxe$S_CN/gxe$S_all))
max((gxe$S_2_no/gxe$S_all))
max((gxe$S_DS/gxe$S_all))
mean((gxe$S_AP/gxe$S_all))
mean((gxe$S_CN/gxe$S_all))
mean((gxe$S_2_no/gxe$S_all)) + mean((gxe$S_DS/gxe$S_all))

AP <- (gxe$S_AP)
CN <- (gxe$S_CN)
DS <- (gxe$S_DS)
twono <- (gxe$S_2_no)
all <- gxe$S_all
diag(twono) <- NA
diag(AP) <- NA
diag(CN) <- NA
diag(DS) <- NA
diag(all) <- NA

median(AP, na.rm = TRUE)
median(CN, na.rm = TRUE)
median(DS, na.rm = TRUE)
median(twono, na.rm = TRUE)
median(all, na.rm = TRUE)

sum(AP, na.rm = TRUE)/sum(diag(all))
sum(CN, na.rm = TRUE)/sum(diag(all))
sum(DS, na.rm = TRUE)/sum(diag(all)) + sum(twono, na.rm = TRUE)/sum(diag(all))
sum(all, na.rm = TRUE)/sum(diag(all))

sum(AP, na.rm = TRUE)/(sum(all, na.rm = TRUE))
#sum(CN, na.rm = TRUE)/(2*sum(all, na.rm = TRUE))
sum(DS, na.rm = TRUE)/(sum(all, na.rm = TRUE))
sum(twono, na.rm = TRUE)/(sum(all, na.rm = TRUE))
sum(all, na.rm = TRUE)/sum(all, na.rm = TRUE)

AP/diag(all)
CN/diag(all)
DS/diag(all)
twono/diag(all)
mean(diag(all))
sum(diag(all))

mean(AP, na.rm = TRUE)
mean(CN, na.rm = TRUE)
mean(DS + twono, na.rm = TRUE) 
mean(twono, na.rm = TRUE)
mean(all, na.rm = TRUE)
7+160+44+76
max(all, na.rm = TRUE)
120+159+7

1.5+33+9+16
```

`r length(get_significant_results(m))` SNPs have significant effects in the mash analysis. Of those, between `r min(gxe$S_AP)` and `r max(gxe$S_AP)` have antagonistically pleiotropic effects between pairs of conditions.

@@

Instead, the vast majority of SNPs have common effects across sites (
`r mean((gxe$S_2_no/gxe$S_all)) + mean((gxe$S_DS/gxe$S_all))`) or are conditionally neutral (`r mean((gxe$S_CN/gxe$S_all))`) ( e.g., having effects at some sites but not others) with only `r mean((gxe$S_AP/gxe$S_all))` showing sign change.
